%!TEX root = ../../luke-sheard-resume.tex

% Dates
\textsc{\small{J.P. Morgan Chase \& Co. }}
\hfill
\textsc{\small{\raggedleft aug '16 -}}

% Title
{\Large Senior Software Engineer}

\vspace{5pt}

{\large Lead - App Frameworks}
\hfill
\textsc{\small{\raggedleft nov '20 - }}

\begin{itemize}
	\item Owning product direction for developer tooling for the Digital Platform group within CIB.
	\item Developed and open sourced \textit{modular} - a CLI for building libraries and applications on top of \textit{esbuild}.
\end{itemize}

{\large Lead - Web Infrastructure}
\hfill
\textsc{\small{\raggedleft dec '19 - nov '20 }}

Working on maintaining and modernizing the infrastructure within in the Athena platform.

\begin{itemize}
	\item Web Infrastructure for 5000+ applications and APIs.
	\item Migration of over 500,000+ jobs to Kubernetes.
\end{itemize}

\vspace{8pt}

{\large Product Engineer - TRM Applications}
\hfill
\textsc{\small{\raggedleft feb - dec '19}}

I was tasked with building the systems to power the new web applications for Athena's TRM (Trade and Risk Management) application suite. This involved building a set of new infrastructure and frameworks for hosting real time pricing models. 

\vspace{8pt}

{\large Markets Web Platform}
\hfill
\textsc{\small{\raggedleft may '17 - feb '19}}

Designed and engineer new platform as a service for TypeScript application development. Developed open source memory filesystem and  integrated into Athena's development environment. 

Created a declarative application deployment and load balancer as a service product for Athena. Hosting 5000+ services and 500+ TypeScript applications.

\vspace{8pt}

{\large Credit Technology}
\hfill
\textsc{\small{\raggedleft aug '16 - may '17}}

\textit{Graduate placement}. I worked on Credit's new intraday risk system. I built the production monitoring for the system and several new web components for display the information. 